---
title: "Task-2 Clustering"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Author- Shivam Khandelwal

### From the Given Iris Dataset, we need to figure out the number of optimal clusters and visualise the result.

#### Importing required Libraries:
```{r cars}
library(datasets)
library(ggplot2)
library(dplyr)
library(factoextra)
library(stats)
library(gridExtra)
library(grid)
```

#### Loading the data and looking for a statistical summary:

```{r pressure}
data("iris")
summary(iris)
```
<p></p>
<p></p>
#### Visualizing the Iris Dataset pattern and detailed visualisation of length and width.

First 10 Rows:
```{r}
head(iris, n=10)
```
<p></p>
<p></p>
#### GridPlot for 4 different boxplots to compare the Sepal and Petal's Length and Width for whole data.

```{r}
p1<- ggplot(iris, aes(Species, Sepal.Length, fill= Species))+geom_boxplot()+theme(legend.position = "none")

p2<- ggplot(iris, aes(Species, Sepal.Width, fill= Species))+geom_boxplot()+theme(legend.position = "none")

p3<- ggplot(iris, aes(Species, Petal.Length, fill= Species))+geom_boxplot()+theme(legend.position = "none")

p4<- ggplot(iris, aes(Species, Petal.Width, fill= Species))+geom_boxplot()+theme(legend.position = "none")

grid.arrange(p1  + ggtitle(""),
             p2  + ggtitle(""),
             p3 + ggtitle(""),
             p4 + ggtitle(""),
             nrow = 2,
             top = textGrob("Sepal and Petal Box Plot", 
                            gp=gpar(fontsize=10))
)

```
<p></p>
<p></p>
#### Visualizing the optimal number of clusters using the Elbow method and we can see the elbow forming at 3 and then "Total Within Sum of Squares" remained almost same and didn't decrease significantly.
```{r}
fviz_nbclust(x = iris[, 3:4],FUNcluster = kmeans, method = 'wss')
```
<p></p>
<p></p>
#### Defining the kmeans algorithm and setting clusters to be 3
```{r}
clusters<- kmeans(iris[, 3:4], 3, nstart = 1)
```
<p></p>
<p></p>

#### Now Visualising these clusters to see the details of the dataset and how the clusters are formed.
```{r}
fviz_cluster(clusters, data = iris[, 3:4])
```



